Reducing iptables configuration complexity using chains

### 2014-05-07 iptables/presentation.tex
add 'brief' to introduction
use capitals
add twitter account to first slide
fix cc position
use term 'use 'case'
fix grammar

\institute[UGent]{Ghent University, Belgium}

@@

      \item introduction to iptables
      \item optimizing configuration with an example setup
      \item conclusions

@@

    All rules are checked one for one, and if one matches the target is executed :

@@

    \frametitle{Tutorial example : setup}

@@

    \frametitle{Tutorial example : webserver}

@@

    \frametitle{Tutorial example : sysadmin PCs}

@@

    \frametitle{Tutorial example : webmaster PCs}

@@

    \frametitle{Tutorial example : access to SMB}

>>>>

\institute[UGent]{@dcadriaenssens - Ghent University, Belgium}

@@

      \item Brief introduction to iptables
      \item Optimizing configuration with a tutorial use case
      \item Conclusion

@@

    All rules are checked one by one, and if one matches the target is executed :

@@

    \frametitle{Tutorial use case : setup}

@@

    \frametitle{Tutorial use case : webserver}

@@

    \frametitle{Tutorial use case : sysadmin PCs}

@@

    \frametitle{Tutorial use case : webmaster PCs}

@@

    \frametitle{Tutorial use case : access to SMB}
